---
title: 'Class 6: R Functions'
author: "Jinyoung Park"
date: "1/23/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions 

## Level 2 heading 

### Level 3 heading


plot(1:5, col = "blue")
```{r}
#This is a silly plot
plot(1:5, col = "blue")
```


Lets see more about **file import** (i.e. reading fiels into R). The main read function in base R is `read.table()`

```{r}
t1 <- read.table("test1.txt")
```

We need to add arguments to get this file imported 

```{r}
t1 <- read.table("test1.txt", sep=",", header = TRUE)
```

Or I could just use `read.csv()` which has the arguments I want in this case!

```{r}
t1 <- read.csv("test1.txt")
```

```{r}
read.table("test1.txt", sep="$", header = TRUE)
```

Our first example function:

```{r}
add <- function(x, y=1) {
  #Sum the imput x and y
  x+y
}
```

Let's try using this function 

```{r}
add(7,3)
```

How does this work with vectors as input.

```{r}
add(c(1,2,4))
```


```{r}
add(c(1,2,4), 4)
```

```{r}
add(c(1,2,4), c(1,2,4))
```

```{r}
add(c(1,2,4), c(1,2,4))
```


What is this `range()` function you talk of? 
```{r}
x <- c(4,4,10,3,11)
max(x)
min(x)
```

```{r}
range(x)
```

This is our second function
```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale(x)
```

Do some more testing
```{r}
rescale(1:10)
```

```{r}
# How would you get your function to work here...
rescale(c(1,2,NA,3,10))
```

```{r}
x <- c(1,2,NA,3,10)
rng <- range(x)
rng
```

```{r}
rng <- range(x, na.rm=TRUE)
rng
```

```{r}
rescale2 <- function(x) {
 rng <-range(x, na.rm = TRUE)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

```{r}
rescale2(c(1,2,NA,3,10))
```

Going too far!
```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
  
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 
 print("is it me you are looking for?")
 
 if(plot) {
 plot(answer, typ="b", lwd=4)
   
 }
 print("I can see it in ...")
 return(answer)
}
```

```{r}
rescale3(x, plot = TRUE)
```

Hands on section B.

```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="o", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="o", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="o", ylab="Bfactor")
```

> Q1. What type of object is returned from the read.pdb() function? 

It is a list of 8 things and of class "pdb", "sse"
```{r}
class(s1)
```

```{r}
str(s1)
```

```{r}
aa321(s1$seqres)
```

```{r}
s1$atom
```


```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, typ="l", col="blue", lwd=2)
points(s3.b, typ="l", col="red", lwd=2)
```


```{r}
hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) ) 
plot(hc)
```







> QUESTION 6

```{r}
# Can you improve this analysis code?
library(bio3d)

s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

## four lines of codes are repeated
s1 <- read.pdb(“4AKE”)
s1.chainA <- trim.pdb(s1, chain = “A”, elety = “CA”)
s1.b <- s1.chainAatomb s1.chainA$atom
plotb3(s1.b, sse = s1.chainA, typ = “l”, ylab = “Bfactor”)

## Turn this into a new function, drug_interaction_plot.

drug_interaction_plot brings in a vector from PDB files along with the parameters to analyze different files including chain, element, and factor.  

This new function works with any vector from PDB files. It creates the first plot with the first vector with applied parameters and adds other plots to the existing plot.  

To make it easier to visualize, the output is one plot with different colored line for each file. Like plot of original analysis code, the residues are on the x-axis and the specified factor on the y-axis. 


```{r}
drug_interaction_plot <- function(file, chain, elmnt, fctr) {
  
  # makes data different colors in the graph
  plot_colors <- c("pink", "lightblue", "lightgreen")
  
  # to repeat through every file vector
  for (i in 1:length(file)) {
  s1 <- read.pdb(file[i])

  s1.chain <- trim.pdb(s1, chain = chain, elety = elmnt)
  
  atom_df <- s1.chain$atom
  
  # the "$" syntax cannot take a variable, so s1.fctr takes in all the atom information and selects an entire column based on the factor input
  s1.fctr <- atom_df[, fctr] 
  
  # creates the first plot
  if (i == 1) {
    plotb3(s1.fctr, sse = s1.chain, typ = "l", ylab = paste(toupper(fctr), "factor", sep = ""), col = plot_colors[i])
    
  # adds additional plots to first plot
  } else {
    lines(s1.fctr, col = plot_colors[i])
  }
  }
  
  # creates a legend for the graph
  legend("topright", title = "PDB File Name", file, fill = plot_colors, horiz=TRUE, cex = 0.5, inset = c(0.05, 0.05))
}
```

##Test the function with three files with parameters of chain "A", elements "CA", and factors "b".

```{r}
files <- c("4AKE", "1AKE", "1E4Y")
chains <- "A"
elements <- "CA"
factors <- "b"

drug_interaction_plot(files, chains, elements, factors)
```

