---
title: "Lecture 6 Homework"
author: "Jinyoung Park"
date: "1/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Given Code
```{r}
# Can you improve this analysis code?
library(bio3d)

s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

# How would you generalize the original code above to work with any set of input protein structures?

## Which codes are repeated?
s1 <- read.pdb(“4AKE”)

s1.chainA <- trim.pdb(s1, chain = “A”, elety = “CA”)

s1.b <- s1.chainAatomb s1.chainA$atom

plotb3(s1.b, sse = s1.chainA, typ = “l”, ylab = “Bfactor”)

## Turn this into a new function, drug_interaction_plot.

drug_interaction_plot brings in a vector from PDB files along with the parameters to analyze different files including chain, element, and factor.  

This new function works with any vector from PDB files. It creates the first plot with the first vector with applied parameters and adds other plots to the existing plot.  

To make it easier to visualize, the output is one plot with different colored line for each file. Like plot of original analysis code, the residues are on the x-axis and the specified factor on the y-axis. 

```{r}
drug_interaction_plot <- function(file, chain, elmnt, fctr) {
  
  # makes data different colors in the graph
  plot_colors <- c("pink", "lightblue", "lightgreen")
  
  # to repeat through every file vector
  for (i in 1:length(file)) {
  s1 <- read.pdb(file[i])

  s1.chain <- trim.pdb(s1, chain = chain, elety = elmnt)
  
  atom_df <- s1.chain$atom
  
  # the "$" syntax cannot take a variable, so s1.fctr takes in all the atom information and selects an entire column based on the factor input
  s1.fctr <- atom_df[, fctr] 
  
  # creates the first plot
  if (i == 1) {
    plotb3(s1.fctr, sse = s1.chain, typ = "l", ylab = paste(toupper(fctr), "factor", sep = ""), col = plot_colors[i])
    
  # adds additional plots to first plot
  } else {
    lines(s1.fctr, col = plot_colors[i])
  }
  }
  
  # creates a legend for the graph
  legend("topright", title = "PDB File Name", file, fill = plot_colors, horiz=TRUE, cex = 0.5, inset = c(0.05, 0.05))
}
```

## Test the function with three files with parameters of chain "A", elements "CA", and factors "b".

```{r}
files <- c("4AKE", "1AKE", "1E4Y")
chains <- "A"
elements <- "CA"
factors <- "b"

drug_interaction_plot(files, chains, elements, factors)
```